\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-02-28 reviews/response.Rmd

# Reviewer 1 comments {-}

# Reviewer 2 comments {-}

> p.10, l.1-15 It wasn't clear to me why the subtraction was performed in the equation (2) because I couldn't find any description for the global coordinate system of the canvas. The value of y could be negative. Please add the description how to deal with the coordinate system, especially the y-axis.

The reason why the subtraction is performed was originally given in the following paragraph of Equation (2).

# Reviewer 3 comments {-}

> p1, l32: "information, and events." - remove the comma

We have removed the comma and elsewhere, and adjusted the language based on the comments.

> p2, l9: "grammar of graphics" - provide reference immediately here and not only later in the article and explain what the grammar of graphics is; also "piped into" may not be understood by outsiders

Done.

> Fig.1 (& related figs): I suppose you use a "3-class Dark2" color scheme from Rcolorbrewer? This does not work well when printed in grayscale: The colors become almost indistinguishable. ...

We have changed the colour scheme from "Dark2" to "4-class PuOr" (without faint orange) in Figure 1 and all consecutive figures.

> Fig.4: Colors orange & purple are hard to distinguish in grayscale. Moreover, you should use different colors here as these 2 colors are already related to the 3 stations.

We have changed the colour to red and blue picked from a "4-class RdYlBu" colour scheme, which is different from the colours used for the 3 stations.

> Fig.2: Instead of "Jan 2016" ... "Jan 2017", be specific and list "Jan 1, 2016" ... "Jan 1, 2017"

Done.

> Fig.2: Can you match the minor gridlines with the start of a month, rather than the middle of a month? This will make it much easier to identify the approximate dates for some of the other spikes. No need to label these minor gridlines.

Done.

> Fig.2: You mention "small multiples" only in a figure caption. This concept is a central
part of your calendar graphics and should be summarized in more details (including references) in the main text. Also mention Unwin & Valero-Mora's "Ensemble Graphics", JCGS, 27(1), as a major concept that applies to both sets of related figures in your article.

ToDo

> Fig.3: Add ticmarks at 0 and 24. See whether ticmark labels fit. If not, OK to omit those for 0 and 24.

Done.

### 2019-02-28 main.Rmd
revision

We develop a method for organizing and visualizing temporal data, collected at sub-daily intervals, into a calendar layout. The calendar format is created using linear algebra, giving a restructuring of the data, that can then be piped into grammar of graphics definitions of plots [@wilkinson2006grammar; @wickham2009ggplot2], as used in **ggplot2** [@R-ggplot2]. The data restructuring approach is consistent with the tidy data principles available in the **tidyverse** [@R-tidyverse] suite. The methods are implemented in a new R package called **sugrrants** [@R-sugrrants].

>>>>

We develop a method for organizing and visualizing temporal data, collected at sub-daily intervals, into a calendar layout. The calendar format is created using linear algebra, giving a restructuring of the data, that can then be integrated into a data pipeline. The core component of the pipeline is to visualise the resulting data using the grammar of graphics [@wilkinson2006grammar; @wickham2009ggplot2], as used in **ggplot2** [@R-ggplot2], which defines plots as a functional mapping from data points to graphical primitives. The data restructuring approach is consistent with the tidy data principles available in the **tidyverse** [@R-tidyverse] suite. The methods are implemented in a new R package called **sugrrants** [@R-sugrrants].

### 2019-02-28 main.tex
changed colour palatte according to reviewer 3
chinese embedded using showtext
revision

We develop a method for organizing and visualizing temporal data,
collected at sub-daily intervals, into a calendar layout. The calendar
format is created using linear algebra, giving a restructuring of the
data, that can then be piped into grammar of graphics definitions of
plots \citep{wilkinson2006grammar, wickham2009ggplot2}, as used in
\textbf{ggplot2} \citep{R-ggplot2}. The data restructuring approach is
consistent with the tidy data principles available in the
\textbf{tidyverse} \citep{R-tidyverse} suite. The methods are
implemented in a new R package called \textbf{sugrrants}
\citep{R-sugrrants}.

@@

{\centering \includegraphics[width=\textwidth]{img/chn-1-embedded}

@@

>>>>

We develop a method for organizing and visualizing temporal data,
collected at sub-daily intervals, into a calendar layout. The calendar
format is created using linear algebra, giving a restructuring of the
data, that can then be integrated into a data pipeline. The core
component of the pipeline is to visualise the resulting data using the
grammar of graphics \citep{wilkinson2006grammar, wickham2009ggplot2}, as
used in \textbf{ggplot2} \citep{R-ggplot2}, which defines plots as a
functional mapping from data points to graphical primitives. The data
restructuring approach is consistent with the tidy data principles
available in the \textbf{tidyverse} \citep{R-tidyverse} suite. The
methods are implemented in a new R package called \textbf{sugrrants}
\citep{R-sugrrants}.

@@

{\centering \includegraphics[width=\textwidth]{figure/chn-1}

@@

\hypertarget{reasons-to-use-calendar-based-displays}{%
\subsection{Reasons to use calendar-based
displays}\label{reasons-to-use-calendar-based-displays}}
